Viscous Erosion in Porous Media

### 2018-03-25 docs/methods/erosion_methods.tex
NM

The corresponding stream function is biharmonic, $\Delta^2 \psi = 0$, and the ansatz $\psi = r^{\lambda}f(\theta)$ gives the 4th-order ODE~\cite{poz1997}
\begin{align}
\label{fODE}
f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0.
\end{align}
This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$. For arbitrary opening angle $\beta$, ODE \eqref{fODE} and its boundary conditions constitute an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$. We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and thus set $\lambda = 2$. The corresponding solution to \eqref{fODE} that satisfies odd symmetry is given by
\begin{align}
  f(\theta) = B \sin (2 \theta) + C \theta \, ,
\end{align}
and imposing the no-slip boundary conditions gives the condition
\begin{align}
  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0 \, .
\end{align}
This nonlinear equation has solution $\thb \approx 129^\circ$, which gives the uniform-stress opening angle as $\oangle \approx 102^\circ$ degrees. 
% Pozrikidis page 239: symmetric flow.

>>>>

The corresponding stream function is biharmonic, $\Delta^2 \psi = 0$, and the ansatz $\psi = r^{\lambda}f(\theta)$ gives the 4th-order ODE~\cite{poz1997}
\begin{align}
\label{fODE}
f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0.
\end{align}
This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$ and odd symmetry about the horizontal axis, $f(0) = f''(0) = 0$. For arbitrary opening angle, ODE \eqref{fODE} and the boundary conditions comprise an eigenvalue problem for $\lambda$, whose solution furnishes the stream function and the corresponding shear stress on the wedge surface $\tau = \mu r^{\lambda-2} f''(\thb)$. We, however, seek to determine the particular opening angle that produces {\em uniform} shear stress and therefore set $\lambda = 2$.
The odd-symmetric solution to \eqref{fODE} that corresponds to $\lambda=2$ is given by
\begin{align}
  f(\theta) = B \sin (2 \theta) + C \theta \, .
\end{align}
Imposing the no-slip boundary conditions gives the condition
\begin{align}
  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0 \, .
\end{align}
This nonlinear equation has solution $\thb \approx 129^\circ$, which implies that the the uniform-stress wedge has an opening angle of $\oangle \approx 102^\circ$.
% Pozrikidis page 239: symmetric flow.

We comment
